### 2023-03-18 notebooks/fidelity.qmd
more work on notebook

# Plots:
plts = []
for name ∈ ordered_names
    ce = counterfactuals[name]
    plt = plot(ce; title=name, colorbar=false, ticks = false, legend=false, zoom=0)
    plts = vcat(plts..., plt)
end
_n = length(generators)
plot(plts..., size=(_n * img_height,1.05*img_height), layout=(1,_n))
```

>>>>

# Plots:
plts = []
for name ∈ ordered_names
    ce = counterfactuals[name]
    plt = plot(ce; title=name, colorbar=false, ticks = false, legend=false, zoom=-0.5)
    if :energy_sampler ∈ collect(keys(ce.params))
        Xgen = ce.params[:energy_sampler].buffer
        scatter!(Xgen[1,:],Xgen[2,:],alpha=0.5,color=target,shape=:star,label="X|y=$target")
    end
    plts = vcat(plts..., plt)
end
_n = length(generators)
plot(plts..., size=(_n * img_height,1.05*img_height), layout=(1,_n))
```
